\problemname{The Gourmet}
The French gourmet Frank is a very well-respected gourmet; his job involves going around to various restaurants, eating their food and then writing a review about the restaurant.
But he carries a dark secret: he is actually only interested in eating as much as possible and in any order!

However, Frank understands that a true gourmet can't eat in just any manner, like starting with his dessert and finishing with a salad.
Therefore, he asks for your help in constructing a list with all the different ways he could arrange his courses during a meal, so that he can pick the best order.

During the serving, Frank has $M$ minutes to eat.
The restaurant offers $N$ different courses, and he can eat any number of servings of each course.
For course $i$, it takes $T_i$ minutes to eat a serving of it.
Frank wants to eat something during each of the $M$ minutes he has, and he wants to finish every course that he is served.
He never wants to start eating a new course until he finished the last one.

Your task is to write a program to compute the number of ways he could arrange his meal, given these restrictions.

\section*{Input}
The first line contains an integer $M$ ($1 \le M \le 1\,000$), the number of minutes. 

The second line contains an integer $N$ ($1 \le N \le 30$), the number of courses.

Afterwards, $N$ lines follow with an integer $T_i$ ($1 \le T_i \le 200$) on each line, the time it takes to eat every dish.

\section*{Output}
The program should output the number of ways in which Frank can eat during exactly $M$ minutes.

The answer will always be at most 2 billion ($2\,000\,000\,000$).

\section*{Scoring}
Your solution will be tested on a set of test case groups.
To get the points for a group, you need to pass all the test cases in the group.

\noindent
\begin{tabular}{| l | l | p{10cm} |}
\hline
Group & Points & Constraints \\ \hline
$1$    & $60$        & The answer will be less than $2$ million ($2\,000\,000$). \\ \hline 
$2$    & $40$        & No additional constraints \\ \hline
\end{tabular}

\section*{Explanation of Sample $1$}
Frank is going to eat during $10$ minutes and have two courses to choose from, for example a salad (takes $3$ minutes to eat) and pie ($7$ minutes).
There are only two ways he can eat them: first pie and then salad or vice versa.
If he only eats salad he will either finish too quickly ($3 \text{ servings} = 9 \text{ minutes}$) or too late ($4 \text{ servings} = 12 \text{ minutes}$).
